---
title: "A2 Assignment - Refugee Analysis"
author: "MBAN - Group 7"
output:
  pdf_document: default
  html_document: default
---

### Team Members:  

Abi Joshua GEORG / Eri Yoshimoto / Hakeem GARCIA \newline
Nattida TAVAROJN / Neha NAGABHUSHAN / Weikang YANG

## Introduction

Refugee migration has been a significant global issue, with various countries experiencing fluctuations in the number of people seeking asylum. This report analyzes refugee data from multiple countries over a span of years to identify trends, patterns, and key insights. The study involves data cleaning, transformation, visualization, and statistical analysis to gain a deeper understanding of global refugee movements.

## Data Preparation and Cleaning
The dataset initially contained raw refugee statistics, which required significant cleaning before analysis.
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)
# read data from database
raw_df <- read_csv("data/A2_refugee_status.csv", col_types = cols(.default = "c"))
```

### Handling Missing and Inconsistent Values

The dataset contained placeholders for missing values, such as "D," "X," and "-", which were converted to "0."
Numeric values were reformatted by removing commas and converting them into numerical data types.
```{r, message=FALSE, warning=FALSE}
# Set NULL value("D", "X", "-")as "0"
raw_df[raw_df == "D" | raw_df == "X" | raw_df == "-"] <- "0"
# set the value column as numbers value and delete comma and transfer to numeric value
raw_df[ , -1] <- lapply(raw_df[ , -1], function(x) as.numeric(gsub(",", "", x)))
# set cleaned data frame as df and use df in later operation
# combine "Congo, Democratic Republic" and "Congo, Republic"
congo_rows <- raw_df %>% filter(`Continent/Country of Nationality` %in% 
                                  c("Congo, Democratic Republic", "Congo, Republic"))
congo_sum <- colSums(congo_rows[, -1], na.rm = TRUE)

#  remove the original duplicated Congo data
raw_df <- raw_df %>% filter(!`Continent/Country of Nationality` %in% 
                              c("Congo, Democratic Republic", "Congo, Republic"))

# add the new combined Congo data to the data frame
raw_df <- raw_df %>%
  add_row(`Continent/Country of Nationality` = "Congo", !!!as.list(congo_sum))
```
### Standardizing Country Names

Countries with alternative naming conventions, such as "China, People's Republic" and "Korea, North," were renamed to "China" and "North Korea" for consistency.

```{r, message=FALSE, warning=FALSE}
# Replace the Countries' name with formal format
country_df <- raw_df %>%
  mutate(`Continent/Country of Nationality` = case_when(
    `Continent/Country of Nationality` == "China, People's Republic" ~ "China",
    `Continent/Country of Nationality` == "Korea, North" ~ "North Korea",
    TRUE ~ `Continent/Country of Nationality`
  ))
df <- country_df
```


```{r, message=FALSE, warning=FALSE}
# create the new dataframe 'contry_df',and remove the un-country row from the dataframe
# defined the name list that will be removed from the dataframe
non_countries <- c("Africa", "Asia", "Europe", "North America", 
                   "Oceania", "South America", "Unknown", "Other", "Total")

# use filter to get the row that will be delete
removed_countries <- df %>% 
  filter(`Continent/Country of Nationality` %in% non_countries)

# create a new dataframe that only containt the 'countries'
country_df <- df %>%
  filter(!`Continent/Country of Nationality` %in% non_countries)

# print the row that be deleted to make sure all of them are 'non-countries'
print("delete rows with non-contry:")
print(removed_countries$`Continent/Country of Nationality`)

# check the new dataframe
head(country_df)
```
## Trends in Refugee Migration

### 1. Overall Refugee Trends by Country

A line chart visualizes the refugee numbers from each country over time.

```{r, message=FALSE, warning=FALSE}  
library(ggplot2)
library(dplyr)
library(tidyr)

country_long <- country_df %>%
  pivot_longer(cols = -`Continent/Country of Nationality`, 
               names_to = "Year", values_to = "Value") %>%
  mutate(
    Year = as.numeric(Year),
    Value = as.numeric(Value)
  )

# filter the top 5 for each year
top_countries_per_year <- country_long %>%
  group_by(Year) %>%
  arrange(desc(Value)) %>%
  slice_head(n = 5)

# plot the line chart
ggplot(top_countries_per_year, aes(x = Year, y = Value, color = `Continent/Country of Nationality`, group = `Continent/Country of Nationality`)) +
  geom_line(size = 1) +
  theme_minimal() +
  labs(
    title = "Top 10 Refugee Countries Each Year",
    x = "Years",
    y = "Number of Refugees",
    color = "Countries"
  ) +
  scale_x_continuous(limits = c(2005, 2016), breaks = 2005:2016) +
  theme(
    legend.position = "right",
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(size = 10)
  )

```
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

# 将数据转换为长格式
country_long <- country_df %>%
  pivot_longer(cols = -`Continent/Country of Nationality`, 
               names_to = "Year", values_to = "Value") %>%
  mutate(
    Year = as.numeric(Year),
    Value = as.numeric(Value)
  )

# 筛选每年的前十个国家
top_countries_per_year <- country_long %>%
  group_by(Year) %>%
  arrange(desc(Value)) %>%  # 按难民数量降序排列
  slice_head(n = 5)  # 取前十个国家

# 绘制折线图
ggplot(top_countries_per_year, aes(x = Year, y = Value, color = `Continent/Country of Nationality`, group = `Continent/Country of Nationality`)) +
  geom_line(size = 1) +
  theme_minimal() +
  labs(
    title = "Top 10 Refugee Countries Each Year",
    x = "Years",
    y = "Number of Refugees",
    color = "Countries"
  ) +
  scale_fill_manual(
    name = "Legend", 
    values = c(
     "#556b84",  
     "#d4a373", 
     "#a8b89a",  
     "#a29bb3",
     "#d49391",
     "#e5d5b2",
     "#98c4c1",
     "#b8a38b"
    )
  ) +
  scale_x_continuous(limits = c(2005, 2016), breaks = 2005:2016) +
  theme(
    legend.position = "right",
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(size = 10)
  )

```

```{r, message=FALSE, warning=FALSE}
# Calculate the number of refugees for each state by year
continent_df <- df %>%
  filter(`Continent/Country of Nationality` %in% c("Africa", "Asia", "Europe", 
                                                   "North America", "Oceania", "South America")) %>%
  pivot_longer(cols = -`Continent/Country of Nationality`, 
               names_to = "Year", values_to = "Value") %>%
  group_by(`Continent/Country of Nationality`, Year) %>%
  summarise(Total_Refugees = sum(Value, na.rm = TRUE))

# make sure the 'year' value is in Number data format
continent_df$Year <- as.numeric(continent_df$Year)

```
###  Refugee Trends Across Presidential Terms (2006–2015)
The analysis of refugee data from 2006 to 2015 provides valuable insights into global migration patterns and highlights the influence of leadership periods on refugee numbers. By combining stacked bar charts with trend lines and presidential term overlays, the visualization effectively tells a compelling story of refugee distribution across continents during the George W. Bush and Barack Obama administrations.

#### Key Insights:

Presidential Term Influence:

##### The data is segmented into two distinct presidential periods:
  - George W. Bush (2006–2008): This period shows a steady increase in refugee numbers, indicating global conflicts or crises that led to heightened migration.
  - Barack Obama (2009–2015): The refugee numbers initially declined but later stabilized at higher levels, reflecting the impact of sustained geopolitical challenges during this time.
  
### Stacked Bar Chart for Continental Trends:

##### The stacked bar chart provides a breakdown of refugee numbers by continent. Notably:
 - Asia and Africa consistently contributed the highest numbers of refugees, driven by ongoing conflicts and socio-political instability.
 - Europe and the Americas saw comparatively smaller contributions, reflecting differences in regional refugee patterns. 

```{r}
library(ggplot2)
library(dplyr)

presidents <- data.frame(
  President = c("G. W. Bush", "Obama"),
  Start_Year = c(2005, 2009),
  End_Year = c(2009, 2016)
)

continent_df <- continent_df %>%
  mutate(
    Year = as.numeric(Year),
    Total_Refugees = as.numeric(Total_Refugees)
  )


yearly_refugees <- continent_df %>%
  group_by(Year) %>%
  summarise(Total_Refugees = sum(Total_Refugees, na.rm = TRUE))


ggplot() +

  geom_rect(data = presidents, aes(xmin = Start_Year, xmax = End_Year, ymin = 0, ymax = Inf, fill = President), alpha = 0.2) +

  geom_bar(data = continent_df, aes(x = Year, y = Total_Refugees, fill = `Continent/Country of Nationality`), 
           stat = "identity", position = "stack", width = 0.6) +
  geom_line(data = yearly_refugees, aes(x = Year, y = Total_Refugees, group = 1), 
            color = "#9f7abc", size = 2) +
  scale_fill_manual(
    name = "Legend", 
    values = c(
      "G. W. Bush" = "#556b84",  # color the president
      "Obama" = "#d4a373", 
      "Africa" = "#a8b89a",  
      "Asia" = "#a29bb3",
      "Europe" = "#d49391",
      "North America" = "#e5d5b2",
      "Oceania" = "#98c4c1",
      "South America" = "#b8a38b"
    )
  ) +

  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +
  scale_x_continuous(limits = c(2005, 2016), breaks = 2005:2016) +

  theme_minimal() +
  labs(
    title = "Refugee Numbers by Continent (2006-2015) with Presidential Terms",
    x = "Year",
    y = "Total Refugees"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right"
  )

```



```{r, message=FALSE, warning=FALSE}
ggplot(continent_df, aes(x = Year, y = `Continent/Country of Nationality`, fill = Total_Refugees)) +
  geom_tile() +  
  scale_fill_gradient(low = "#556b84", high = "#d4a373") +  # set the color
  theme_minimal() +
  labs(title = "The Heat Map of Refugees for each State Changed by Years",
       x = "Years",
       y = "States",
       fill = "Number of Refugees") +
  theme(legend.position = "right",
        axis.text.y = element_text(size = 10))

```

### 3. Heatmap of Refugee Numbers
```{r, message=FALSE, warning=FALSE}
ggplot(country_long, aes(x = as.numeric(Year), y = `Continent/Country of Nationality`, fill = Value)) +
  geom_tile() +
  scale_fill_gradient(low = "#556b84", high = "#d4a373") +
  theme_minimal() +
  labs(title = "The Number of Refugees for Each Country in Each Year",
       x = "Years",
       y = "Countries",
       fill = "Number of Refugees") +
  theme(legend.position = "right",
  axis.text.y = element_text(size = 5))

```
```{r, message=FALSE, warning=FALSE}
# Calculate the number of Refugees for each country in Total
top_countries <- country_long %>%
  group_by(`Continent/Country of Nationality`) %>%
  summarise(Total_Refugees = sum(Value, na.rm = TRUE)) %>%
  arrange(desc(Total_Refugees)) %>%
  slice_head(n = 10)  #  pick top 10

# get the name of country in top 10
top_country_names <- top_countries$`Continent/Country of Nationality`

# filter the data with top 10
filtered_df <- country_long %>%
  filter(`Continent/Country of Nationality` %in% top_country_names)

ggplot(filtered_df, aes(x = as.numeric(Year), y = `Continent/Country of Nationality`, fill = Value)) +
  geom_tile() +
  scale_fill_gradient(low = "#556b84", high = "#d4a373") +
  scale_x_continuous(limits = c(2005, 2016), breaks = 2005:2016) +
  theme_minimal() +
  labs(title = "The Heat Map of number of Refugees for top 10 Countries",
       x = "Years",
       y = "Countries",
       fill = "Number of Refugees") +
  theme(legend.position = "right",
        axis.text.y = element_text(size = 10))  



```

### The World Map with Refugees number 
```{r, message=FALSE, warning=FALSE}   
library(gganimate)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(gifski)
library(transformr)

country_long <- country_df %>%
  pivot_longer(cols = -`Continent/Country of Nationality`, 
               names_to = "Year", values_to = "Value")
country_long$Year <- as.numeric(country_long$Year)


# load the world map
world_map <- ne_countries(scale = "medium", returnclass = "sf")

# adjust the name of countries
country_long <- country_long %>%
  rename(country = `Continent/Country of Nationality`)

# combine the map data and refugees data
map_data <- world_map %>%
  left_join(country_long, by = c("name" = "country"))

```


```{r}
library(ggplot2)
library(sf)
library(dplyr)

# 
country_long$Year <- as.numeric(country_long$Year)

#
plot_yearly_maps <- function(year) {
  yearly_data <- map_data %>% filter(Year == year)
  
  ggplot() +
    geom_sf(data = world_map, fill = "gray90", color = "white") +
    geom_sf(data = yearly_data, aes(fill = Value), color = "black") +
    scale_fill_gradient(low = "#556b84", high = "#d4a373", na.value = "gray90") +
    theme_minimal() +
    labs(title = paste("Global Refugee Map - Year", year), fill = "Number of Refugees")
}

# 
plot_yearly_maps(2006)
plot_yearly_maps(2007)
plot_yearly_maps(2008)
plot_yearly_maps(2009)
plot_yearly_maps(2010)
plot_yearly_maps(2011)
plot_yearly_maps(2012)
plot_yearly_maps(2013)
plot_yearly_maps(2014)
plot_yearly_maps(2015)
```





#### below code is for generate the GIF

library(gganimate)

p <- ggplot() +
  geom_sf(data = world_map, fill = "gray90", color = "white") +  # the world map
  geom_sf(data = map_data, aes(fill = Value), color = "black") +  # data refugees
  scale_fill_gradient(low = "blue", high = "yellow", na.value = "gray90") + 
  theme_minimal() +
  labs(title = "Global Refugees data Map (Year: {frame_time})",
       fill = "Number of Refugees",
       x = "", y = "") +
  transition_time(Year) +  # change the plot by year
  ease_aes('linear')  # change smoothly

# generate the GIF
anim <- animate(p, duration = 10, fps = 40, width = 800, height = 500, renderer = gifski_renderer())
anim_save("refugees_map_smooth.gif", animation = anim)





## Conclusion

This analysis provides a comprehensive look at global refugee movements, highlighting key trends, high-risk regions, and changes over time. The combination of data cleaning, visualization, and statistical analysis allows for an in-depth understanding of the factors driving refugee migration, which can support future policy-making and humanitarian efforts.
